---
title: "STAT184 Final project"
output: html_notebook
---
# Analysis for coronavirus data.

# https://en.wikipedia.org/wiki/List_of_U.S._states_and_territories_by_GDP

library(readr)
us_states <- read_csv("us-states.csv")
View(us_states)
```{r}
# reade the packages into r notebook
library(readr)
library(tidyverse)
library(ggplot2)
```

```{r}
us_states_cases <- read_csv("us-states.csv")
us_doctornum <- read_csv("us_doctor.csv")
```


```{r}
us_states_cases%>%
  tail(10)
us_states_cases%>%
  glimpse()
```

```{r}
us_doctornum%>%
  head(10)
us_doctornum%>%
  glimpse()
```
```{r}
new_data<-us_states_cases%>%
  filter(date == "2020-04-18")
sum(new_data$cases)
```
```{r}
penn_cases<- us_states_cases%>%
  filter(state == "Pennsylvania")
penn_cases%>%
  ggplot(aes(x= date, y = deaths))+
  geom_col()+
  geom_line(aes(y=cases))
```


```{r}

```

```{r}
us_states_cases%>%
  arrange(desc(cases))%>%
  distinct(state)
```


```{r}
top5_states <-us_states_cases %>%
  filter( grepl( "^New York",state) |grepl( "^New Jersey",state)|grepl( "^Pennsylvania",state)|grepl( "^Massachusetts",state)|grepl( "^California",state))
top5_states %>%
  ggplot(aes(x=date, y = (cases), group = state)) +
  geom_line(aes(color=state))
  
```



```{r}
us_doctornum[,"doctor_condition"] <- NA
for(i in 1:nrow(us_doctornum)) {
    if (us_doctornum[i,2]>350){
      us_doctornum[i,3]<-"high"
    }
    
}
```

```{r}

us_doctornum
```

```{r}

```

```{r}

```

```{r}

```

```{r}

```
```{r}

```


```{r}

```

```{r}

```

```{r}

```